---
title: "Getting Started with neuro2"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with neuro2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(neuro2)
```

# Introduction

The `neuro2` package provides tools for generating comprehensive neuropsychological reports using Quarto and Typst templates. This vignette demonstrates the basic workflow for creating reports from neuropsychological test data.

## Key Features

- **Automated report generation** from neuropsychological test data
- **Domain-specific processing** for cognitive domains (IQ, memory, executive function, etc.)
- **Flexible templates** supporting multiple output formats (HTML, PDF, Typst)
- **Standardized reporting** following clinical best practices

## Basic Workflow

### 1. Check Dependencies

Before using the package, ensure all required dependencies are installed:

```{r eval=FALSE}
check_dependencies()
```

### 2. Prepare Your Data

The package accepts neuropsychological data in CSV or RDA format. Your data should include test results organized by cognitive domains.

```{r eval=FALSE}
# Example data structure
data_file <- system.file(
  "extdata",
  "neurocog.rda",
  package = "neuro2"
)
```

### 3. Process Domain Data

Process your neuropsychological data by cognitive domains:

```{r eval=FALSE}
processed_data <- process_domains(data_file)
```

### 4. Generate Report

Create a comprehensive neuropsychological report:

```{r eval=FALSE}
report_file <- generate_report(
  data_file = data_file,
  template_name = "report-template",
  output_dir = "output",
  output_format = "html"
)
```

## Available Templates

The package includes several templates:

- `report-template`: Comprehensive neuropsychological report
- `domain-specific`: Individual domain reports
- `feedback`: Client feedback reports

## Cognitive Domains

The package processes the following cognitive domains:

- **IQ**: Intelligence and general cognitive ability
- **Academics**: Reading, writing, and math skills
- **Verbal**: Language and verbal processing
- **Spatial**: Visuospatial and visuoconstructional abilities
- **Memory**: Learning and memory functions
- **Executive**: Executive functions and cognitive control
- **Motor**: Motor and psychomotor functions
- **Social**: Social cognition and emotional processing
- **ADHD**: Attention and hyperactivity measures
- **Emotion**: Emotional and behavioral functioning
- **Adaptive**: Adaptive behavior and daily living skills

## Customization

### Custom Templates

You can create custom templates by placing Quarto (.qmd) files in the `inst/templates/` directory.

### Custom Processing

Domain processing can be customized by modifying the `process_domains()` function or creating domain-specific processing functions.

## Advanced Usage

### Batch Processing

Process multiple reports:

```{r eval=FALSE}
data_files <- list.files("data", pattern = "*.csv", full.names = FALSE)
reports <- lapply(data_files, generate_report)
```

### Custom Output Directories

Organize reports by client or date:

```{r eval=FALSE}
client_dir <- create_output_dir(
  "reports",
  subdirs = c("client_001", "client_002")
)
```

## Troubleshooting

### Common Issues

1. **Missing dependencies**: Run `check_dependencies()` to identify missing packages
2. **Data format issues**: Ensure data follows expected structure
3. **Template not found**: Verify template names and locations

### Getting Help

For additional help:

- Check function documentation: `?generate_report`
- View package vignettes: `browseVignettes("neuro2")`
- Report issues on GitHub

## Example Output

When you run `generate_report()`, you'll get a comprehensive neuropsychological report that includes:

- Client demographics and referral information
- Test administration details
- Domain-specific results and interpretations
- Diagnostic impressions
- Recommendations for treatment and accommodations

The report follows professional standards for neuropsychological assessment and can be customized for different clinical contexts.
